### 2017-03-08 manuscript/manuscript.tex
discussion 80%

In addition to the three climate predictors, five shared trends were fit by the most parsimonious DFA model. These represent additional drivers responsible for structuring water temperature across some or all of the 24 sites included in the analysis. Each monitoring sites' factor loading on a particular shared trend indicates the degree to which the trend accounted for variance in T\textsubscript{water} at that site. While the precise identities of these drivers cannot be attained with certainty, they can be inferred through correlation with predictor variables. In this way, we determined the most likely landscape drivers of T\textsubscript{water} to be perennial ice and snow cover, mean watershed slope, and groundwater influx. Slope's likely mechanism of influence is increased turbulence and mixing of water and air in steep, headwater streams, which allows convective warming and cooling to occur more rapidly \colorbox{red}{\lstinline{cite}}.

@@

% fig1: buffering effect is visible as damping followed by jump in RS SD
    SD RS colder throughout the year, less influenced by changes in air.
    % spring snowmelt (hydrograph peak) is the most significant item
    RD actually remains warmer than air throughout the spring, and matches it through July.
% fig2: snow/glac streams are buffered, overall, from temp changes due to air and precip.
    snow isn't signif because of the arrangement of points along the x axis. however, there's a negative
        snowmelt->Twater for the glac streams and a positive one for the RS streams
    Why might each of the landscape predictors be such?
        water table depth: ground water farther from surface, less responsive ground water (to whatever it is)
        BFI: also ground water influx
        ice snow: separation of RD RS?: this could be the rain-on-snow effect
        slope: faster and more turbulent water, greater mixing; also correlated with snow/glac
    what could the other factor be (trend 3)? random error, or a geological or morphological or microclimatic feature not captured by our watershed predictors 
fog3: step through

@@

DFA plots here

>>>>

In addition to the three climate predictors, five shared trends were fit by the most parsimonious DFA model. These represent additional drivers responsible for structuring water temperature across some or all of the 24 sites included in the analysis. Each monitoring sites' factor loading on a particular shared trend indicates the degree to which the trend accounted for variance in T\textsubscript{water} at that site. While the precise identities of these drivers cannot be obtained with certainty, they can be inferred through correlation with predictor variables. In this way, we determined the most likely landscape drivers of T\textsubscript{water} to be perennial ice and snow cover, mean watershed slope, and groundwater influx. In the case of slope, the likely mechanism of influence is increased turbulence and mixing of water and air in steep, headwater streams, which allows convective warming and cooling to occur more rapidly \colorbox{red}{\lstinline{(cite}}; Fig. 3g). As for groundwater, greater influx (represented by baseflow index, or BFI; fig. 3f) corresponds to greater {\it de}-coupling of climatic effects and river temperature, as groundwater should be insulated relative to surface water. For the same reason, greater depth of groundwater should be associated with better insulation and thus further decoupling (Fig. 3d). The buffering effect of perennial ice and snow for SD rivers has already been discussed, but the separation of RD and RS rivers by factor loadings on the associated trend is worth noting (Fig. 3e)

@@

% fig1: buffering effect is visible as damping followed by jump in RS SD
    SD RS colder throughout the year, less influenced by changes in air.
    % spring snowmelt (hydrograph peak) is the most significant item
    RD actually remains warmer than air throughout the spring, and matches it through July.
% fig2: snow/glac streams are buffered, overall, from temp changes due to air and precip.
    snow isn't signif because of the arrangement of points along the x axis. however, there's a negative
        snowmelt->Twater for the glac streams and a positive one for the RS streams
    % Why might each of the landscape predictors be such?
        % water table depth: ground water farther from surface, less responsive ground water (to whatever it is)
        % BFI: also ground water influx
        ice snow: separation of RD RS?: this could be the rain-on-snow effect
        % slope: faster and more turbulent water, greater mixing; also correlated with snow/glac
    what could the other factor be (trend 3)? random error, or a geological or morphological or microclimatic feature not captured by our watershed predictors
fog3: step through

@@

DFA plots here blargenshnargen
